\documentclass{article}

\usepackage{float}
\restylefloat{table}

\usepackage{booktabs}

\title{Team Contributions: Rev 0\\\progname}

\author{\authname}

\date{}

% \input{../Comments}
% \input{../Common}

\begin{document}

\maketitle

\section{Demo Plans}

\wss{

\quad 

Chenwei Song: will demo the forum feature.\\

Qiang Gao: will demoTasks management panel and calendar\\

Qianni Wang: An app quick links feature to access key websites student frequently use, students are able to customize the order of the app icons based on their own experience. A feedback page where students can provide feedback on how to improve our website or university services to help us continuously improve our website and help universities to improve their services. A profile page where user can change their username and see their cGPA from their transcript.\\


Jingyao Qin: After a user uploads a file, use the openai api to extract key course information from the course outline file, display the information on the course details page, and automatically create tasks for the user based on the course assignments mentioned in the outline.

Feature to directly display course information and create course assignments if the course information exists in the database.

Feature to delete a course from the website while deleting the related course assignments at the same time.\\

Shuting Shi: After User enter into the Pomodoro Page, user could click the button to start study. User could choose different music to play as background. After the user finishes a study period of 25 minutes, the screen would generate a tomato in the "harvest blanket".

The weekly achievements could track the pomodoro usage in this week, give a visualization info to users.
}
\section{Meeting Attendance}

\wss{For each team member how many team meetings have they attended since the
POC demo.  This number should be determined from the meeting issues in the
team's repo.  The first entry in the table should be the total number of team
meetings held by the team.}

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Meetings}\\
\midrule
Total & 5\\
Chenwei Song & 5\\
Qiang Gao & 5\\
Qianni Wang & 5\\
Shuting Shi & 5\\
Jingyao Qin & 5\\
\bottomrule
\end{tabular}
\end{table}

\wss{If needed, an explanation for the counts can be provided here.}

\section{Lecture Attendance}

\wss{For each team member how many lectures have they attended since the POC
demo.  This number should be determined from the lecture issues in the team's
repo.  The first entry in the table should be the total number of lectures since
the POC demo.}

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Lectures}\\
\midrule
Total & 2\\
Chenwei Song & 2\\
Qiang Gao & 2\\
Qianni Wang & 2\\
Shuting Shi & 2\\
Jingyao Qin & 2\\
\bottomrule
\end{tabular}
\end{table}

\wss{If needed, an explanation for the lecture attendance can be provided here.}

\section{Commits}

\begin{table}[H]
\centering
\begin{tabular}{lll}
\toprule
\textbf{Student} & \textbf{Commits} & \textbf{Percent}\\
\midrule
Total & 361 & 100\% \\
Chenwei Song & 50 & 13.85\%\\
Qiang Gao & 63 & 17.45\%\\
Qianni Wang & 105 & 29.08\%\\
Shuting Shi & 68 & 18.83\%\\
Jingyao Qin & 75 & 20.77\%\\
\bottomrule
\end{tabular}
\end{table}

\section{Issue Tracker}


\begin{table}[H]
\centering
\begin{tabular}{lll}
\toprule
\textbf{Student} & \textbf{Authored (O+C)} & \textbf{Assigned (C only)}\\
\midrule
Chenwei Song & 16 & 34 \\
Qiang Gao & 5 & 37 \\
Qianni Wang & 52 & 62 \\
Shuting Shi & 14 & 43 \\
Jingyao Qin & 25 & 47 \\
\bottomrule
\end{tabular}
\end{table}


\section{CICD}

In the project's CI/CD pipeline, the Main CI GitHub Action is configured to validate that the Python code adheres to PEP 8 standards, ensuring consistent code style across the project. Additionally, the PR Checks Action verifies that each pull request is properly labeled and linked to relevant issues. This ensures that every PR is easily reviewable and contains sufficient context for team members, aligning with the project's quality expectations and contributing guidelines.
\end{document}